A decomposition based on constrained clustering algorithms for JSP\thanks{Supported by organization x.}

### 2021-10-01 Artificial Intelligence and Machine Learning/PADL_conference/Paper_draft_v1.tex
transpose the table

%\begin{table}
\begin{sidewaystable}
\setlength{\tabcolsep}{5.5pt}
  \begin{center}
    \caption{The performance of selected features.}
    \label{tab4}
%\rotatebox{90}{
 \begin{adjustwidth}{-3.5cm}{}
    \begin{tabular}{c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c | c}

\hline
      \textbf{Instances} & \textbf{FIFO} & \textbf{MTWR} & \textbf{Single-shot} & \textbf{EST} & \textbf{F1} & \textbf{F2} & \textbf{F3} & \textbf{F4} & \textbf{F5} & \textbf{F6} & \textbf{F7} & \textbf{F8} & \textbf{F9} & \textbf{F10} & \textbf{F11} & \textbf{F12} & \textbf{F13} & \textbf{F14} & \textbf{F15}\\
      \hline
      TA51 &3549  &3364  &3632  &3506  &3506  &3362  &3324  &3360  &3346  &\textbf{3294}  &3328  &3588  &3588  &3568  &3514  &3682  &3624  &3554  &3509 \\
      TA52 &3339  &3304  &3615  &3773  &3277  &3318  &3330  &3286  &3243  &3275  &3226  &3397  &3373  &3533  &3256  &3494  &3505  &3373  &\textbf{3184} \\
      TA53 &3160  &3168  &3481  &3478  &3382  &3585  &3347  &3543  &3517  &3250  &3338  &3251  &3522  &3373  &3585  &\textbf{3143}  &3427  &3524  &3380 \\
      TA54 &3218  &3494  &3462  &3497  &3414  &3425  &3425  &3503  &3397  &3265  &3353  &3563  &3443  &3386  &3352  &3270  &3236  &3232  &3289 \\
      TA55 &3291  &3237  &3552  &3482  &3308  &3441  &3424  &3319  &3355  &3386  &3301  &3498  &3385  &3530  &3365  &3309  &3370  &3385  &\textbf{3218} \\
      TA56 &3325  &3287  &3610  &3605  &3353  &3380  &3548  &3270  &3383  &3366  &3564  &\textbf{3229}  &3306  &3362  &3344  &3332  &3338  &3483  &3389 \\
      TA57 &3654  &3633  &3778  &3753  &3605  &3573  &3601  &3583  &3650  &\textbf{3480}  &3592  &3621  &3543  &3608  &3670  &3632  &3749  &3573  &\textbf{3480} \\
      TA58 &3299  &3591  &3718  &3731  &3352  &3412  &3370  &3509  &3707  &3324  &3496  &3517 &3716 &3644  &3611  &3471  &3437  &3365   &3481 \\
      TA59 &3344  &3394  &3613  &3398  &3453  &3416  &3301  &3339  &3508  &3430  &3352  &3258 &3381  &3402  &\textbf{3145}  &3250  &3253  &3284  &3290 \\
      TA60 &3129  &3257  &3550  &3247  &3483  &3315  &3617  &3563  &3591  &3327  &3399  &3374  &3526  &3637  &3425  &3676  &3659  &3767  &3569 \\
\hline
 Average  &3331  &3373  &3601  &3547  &3413  &3423  &3429  &3428  &3470  &3340  &3395  &3430  &3475  &3504  &3427  &3426  &3460  &3454  &3379 \\
\hline
    \end{tabular}
%}
\end{adjustwidth}
  \end{center}
\end{sidewaystable}
%\end{table}

>>>>

\begin{table}
  \begin{center}
    \caption{The performance of selected features.}
    \label{tab4}

    \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l|l|} \hline
      & \multicolumn{11}{|c|}{\textbf{Instances}} \\ \cline{2-12}
      \textbf{Approach}   & TA51                           & TA52                           & TA53                           & TA54 & TA55                           & TA56                           & TA57                           & TA58 & TA59                           & TA60 & AVG  \\ \hline
      \textbf{FIFO}        & 3549                           & 3339                           & 3160                           & 3218 & 3291                           & 3325                           & 3654                           & 3299 & 3344                           & 3129 & 3331 \\
      \textbf{MTWR}        & 3364                           & 3304                           & 3168                           & 3494 & 3237                           & 3287                           & 3633                           & 3591 & 3394                           & 3257 & 3373 \\
      \textbf{Single-shot} & 3632                           & 3615                           & 3481                           & 3462 & 3552                           & 3610                           & 3778                           & 3718 & 3613                           & 3550 & 3601 \\
      \textbf{EST}         & 3506                           & 3773                           & 3478                           & 3497 & 3482                           & 3605                           & 3753                           & 3731 & 3398                           & 3247 & 3547 \\ \hline
      \textbf{F1}          & 3506                           & 3277                           & 3382                           & 3414 & 3308                           & 3353                           & 3605                           & 3352 & 3453                           & 3483 & 3413 \\
      \textbf{F2}          & 3362                           & 3318                           & 3585                           & 3425 & 3441                           & 3380                           & 3573                           & 3412 & 3416                           & 3315 & 3423 \\
      \textbf{F3}          & 3324                           & 3330                           & 3347                           & 3425 & 3424                           & 3548                           & 3601                           & 3370 & 3301                           & 3617 & 3429 \\
      \textbf{F4}          & 3360                           & 3286                           & 3543                           & 3503 & 3319                           & 3270                           & 3583                           & 3509 & 3339                           & 3563 & 3428 \\
      \textbf{F5}          & 3346                           & 3243                           & 3517                           & 3397 & 3355                           & 3383                           & 3650                           & 3707 & 3508                           & 3591 & 3470 \\
      \textbf{F6}          & \textbf{3294} & 3275                           & 3250                           & 3265 & 3386                           & 3366                           & \textbf{3480} & 3324 & 3430                           & 3327 & 3340 \\
      \textbf{F7}          & 3328                           & 3226                           & 3338                           & 3353 & 3301                           & 3564                           & 3592                           & 3496 & 3352                           & 3399 & 3395 \\
      \textbf{F8}          & 3588                           & 3397                           & 3251                           & 3563 & 3498                           & \textbf{3229} & 3621                           & 3517 & 3258                           & 3374 & 3430 \\
      \textbf{F9}          & 3588                           & 3373                           & 3522                           & 3443 & 3385                           & 3306                           & 3543                           & 3716 & 3381                           & 3526 & 3475 \\
      \textbf{F10}         & 3568                           & 3533                           & 3373                           & 3386 & 3530                           & 3362                           & 3608                           & 3644 & 3402                           & 3637 & 3504 \\
      \textbf{F11}         & 3514                           & 3256                           & 3585                           & 3352 & 3365                           & 3344                           & 3670                           & 3611 & \textbf{3145} & 3425 & 3427 \\
      \textbf{F12}         & 3682                           & 3494                           & \textbf{3143} & 3270 & 3309                           & 3332                           & 3632                           & 3471 & 3250                           & 3676 & 3426 \\
      \textbf{F13}         & 3624                           & 3505                           & 3427                           & 3236 & 3370                           & 3338                           & 3749                           & 3437 & 3253                           & 3659 & 3460 \\
      \textbf{F14}         & 3554                           & 3373                           & 3524                           & 3232 & 3385                           & 3483                           & 3573                           & 3365 & 3284                           & 3767 & 3454 \\
      \textbf{F15}         & 3509                           & \textbf{3184} & 3380                           & 3289 & \textbf{3218} & 3389                           & \textbf{3480} & 3481 & 3290                           & 3569 & 3379 \\ \hline
      \end{tabular}
  \end{center}
